---
title: "ggplot training exercises"
output: html_notebook
---
### preparing environment
```{r}
setwd("G:/Meu Drive/5. Cursos/Programacao/Curso R Udemy/bootcampR")

rm(list = ls())

library(tidyverse)
library(ggthemes)

```

```{r}
head(mpg)
```

### histogram of hwy mpg values
```{r}
ggplot(mpg) +
  aes(x = hwy) +
  geom_histogram()
```

### barplot of car counts per manufacturer with color fill defined by cyl count
```{r}
ggplot(mpg) +
  aes(x = manufacturer, fill = factor(cyl)) +
  geom_bar()
```

### switch now to use the txhousing dataset that comes with ggplot2
```{r}
head(txhousing)
```

### create a scatterplot of volume versus sales. Afterwards play around with alpha and color arguments to clarify information.


```{r}
ggplot(txhousing) +
  aes(x = sales, y = volume) +
  geom_point(alpha = 0.5)
```

### add a smooth fit line to the scatterplot from above. Hint: You may need to look up geom_smooth()
```{r}
ggplot(txhousing) +
  aes(x = sales, y = volume) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```




